Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-14 paper/abstraction/appendix.tex
more edits to appendix

\begin{lem} $M$ and $M^A$ have the same set of states. That is, $Q = Q^A$.
    $ $
    \vspace{1em}
    \begin{proof}
      This follows trivially from the construction of $M$.
    \end{proof}
\end{lem}

@@

  We prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
  \begin{proof}
    From Lemma 4, we know that $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since each automata
    shares the same states. Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. However, from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$. Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$. However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
  \end{proof}
\end{lem}

@@

\begin{lem}
  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
  such that $f_{pg}(n) = N$.

  \begin{proof}
    By assumption, we assumed that $f$ is surjective. That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$. 
  \end{proof}

@@

\begin{lem}
  $m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.

  \begin{proof}
    $(\Leftarrow)$

    Suppose we have a simulation relation from the subgraphs rooted at nodes $M$ and $M'$ with $M' \geq_{rank} M$ in the abstract product graph. Assume that $\tilde{M} = f(a)$ and $\tilde{N} = f(b)$. For each neighbor $N'$, if we can make a move from $M'$:

    $$M' \overset{\tilde{N'}}{\rightarrow} N'$$

    then we also make a similar move for $M$ for some $N$ where $N \approx N'$ and $N' \geq_{rank} N$:

    $$M \overset{\tilde{N}}{\rightarrow} N$$

    We must show that the same relation holds for $m$ and $m'$.

    Now assume $m'$ has a neighbor $n'$ where $\tilde{m} = a$ and $\tilde{n} = b$. Then clearly $(a,b)$ is a valid topology edge since it is a transition in the product graph. We now apply the previous lemma with the following facts:

    \[ \begin{array}{ll}
      1. & (a,b) ~\text{is a topology edge} \\
      2. & \tilde{m} = a \\
      3. & f_{pg}(m) = M \\
      4. & (M,N) ~\text{is an edge in}~ PG^A \\
      5. & \tilde{N} = f(b) \\
    \end{array} \]

    This lets us conclude that there exists a node $n'$ such that:

    \[ \begin{array}{ll}
      1. & \tilde{n} = b \\
      2. & f_{pg}(n) = N \\
      3. & (m,n) ~\text{is an edge in}~ PG \\
      4. & P(n) = P(N) \\
    \end{array} \]

    Thus if we have $m' \overset{b}{\rightarrow} n'$, then we also have $m \overset{b}{\rightarrow} n$. The previous lemma can also be used to show that $P(n') = P(N')$ in a symmetric fashion, so we are guaranteed that $n' \geq_{rank} n$ from the fact that $N' \geq_{rank} N$.

@@

  \begin{proof}
    $(\Rightarrow)$

    This is the simpler case. We assume we have $m' \overset{b}{\rightarrow} n'$ implies $m \overset{b}{\rightarrow} n$.
    Simply take $N = f_{pg}(n)$ and $N' = f_{pg}(n')$. If we know that $M' \overset{b}{\rightarrow} N'$ then we already know that $M \overset{b}{\rightarrow} N$ from the homomorphism. All that's required is to show that $N' \geq_{rank} N$. This follows trivially from the fact that $P(n) = P(N)$ and $P(n') = P(N')$.
  \end{proof}

@@

\vspace{1em}
\begin{defn}
  Assign $ord(m) = ord^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly $ord(m) \leq ord(m') \iff m \leq m'$ and $ord(f_{pg}(m)) \leq ord(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

\vspace{1em}
\begin{defn}
  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
\end{defn}

\vspace{1em}
\subsection{Substitution}

>>>>

\vspace{.5em}
\begin{lem} $M$ and $M^A$ have the same set of states. That is, $Q = Q^A$.
    $ $
    \vspace{1em}
    \begin{proof}
      This follows trivially from the construction of $M$. States in $M$ are copied over from states in $M^A$.
    \end{proof}
\end{lem}

@@

  Now we prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
  \begin{proof}
    From Lemma 4, we know that $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since each automata
    shares the same states. Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. However, from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$. Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$. However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
  \end{proof}
\end{lem}

@@

%\begin{lem}
%  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
%  such that $f_{pg}(n) = N$.%

%  \begin{proof}
%    By assumption, we assumed that $f$ is surjective. That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$. 
%  \end{proof}
%\end{lem}

@@

\newcommand{\trans}[3]{\ensuremath{#1 \overset{#3}{\rightarrow} #2}}

\begin{lem}
  For any transition $\trans{m}{m'}{l}$ in $PG$, there is a corresponding transition $\trans{f(m)}{f(m')}{f(l)}$ in $PG^A$.
  \begin{proof}
    if $m' = (l, q_1, \ldots, q_n)$, then $f(m') = (f(l), q_1, \ldots, q_n)$. Since there is the edge $(m,m')$ in $PG$, then there is the edge $(f(m),f(m'))$ in $PG^A$. Finally, because $\Topo(f(m')) = f(l)$, there must be a transition $\trans{f(m)}{f(m')}{f(l)}$.
  \end{proof}
\end{lem}

% n --> m'
% m' --> n

\vspace{.4em}
\begin{lem}
  In the concrete product graph, $m \leq m' \iff f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph.
  \begin{proof}
    $ $

    \vspace{1em}
    We show that $\leq$ forms a simulation relation for the subgraph reachable from $m$ and $m'$ in $PG$ iff $\leq$ forms a simulation relation for the subgraph reachable from $f(m)$ and $f(m')$ for $PG^A$. This involves showing that $m \geq_{rank} m' \iff f(m) \geq_{rank} f(m')$, and that 
    for every transition $\trans{m}{n}{l}$ in $PG$ there is a transition $\trans{m'}{n'}{l}$ iff for every transition $\trans{f(m)}{f(n)}{f(l)}$ in $PG^A$ there is a transition $\trans{f(m')}{f(n')}{f(l)}$.

    \vspace{1em}
    \textbf{Case} $(\Rightarrow)$

    Consider the subgraph of $PG$ reachable from $m$ and $m'$. From $m \leq m'$ and the definition of ($\leq$), we know that $m' \geq_{rank} m$.

    %
    From Lemma 6, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
    From Lemma 8, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.

    \vspace{1.2em}
    \textbf{Case} $(\Leftarrow)$

    Let $M = f(m)$ and let $M' = f(m')$.
    Suppose that $M \leq M'$, which means that with $M' \geq_{rank} M$ in the abstract product graph. It also means that, for each neighbor $N'$, if we have the transition: $\trans{M'}{N'}{L}$ then we also have a transition: $\trans{M}{N}{L}$ where $N' \geq_{rank} N$. We must show that the same relation holds for $m$ and $m'$.

    \vspace{1em}
    Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$. \todo{This can be done because $f$ is surjective}. Also assume that $m'$ has a neighbor $n'$. We know that $\Topo(m) = a$ and $\Topo(m') = b$. Clearly $(a,b)$ is a valid concrete topology edge since it is a transition in the product graph between $m$ and $m'$. We now apply Lemma 7 with the following facts:

    \[ \begin{array}{ll}
      1. & (a,b) ~\text{is a concrete topology edge} \\
      2. & \Topo(m) = a \\
      3. & f_{pg}(m) = M \\
      4. & (M,N) ~\text{is an edge in}~ PG^A \\
      5. & \Topo(N) = f(b) \\
    \end{array} \]

    Lemma 7 lets us conclude that there exists a node $n'$ such that:

    \[ \begin{array}{ll}
      1. & \Topo(n) = b \\
      2. & f_{pg}(n) = N \\
      3. & (m,n) ~\text{is an edge in}~ PG \\
      4. & \Rank(n) = \Rank(N) \\
    \end{array} \]

    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. Lemma 6 together with the assumption $N' \geq N$ shows that $n' \geq{rank} n$.

@@

@@

The previous lemma tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.

\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

\vspace{3em}
\subsection{Constraint Substitution (Part 2)}
